---
title: "Hosting quizzes on shinyapps.io"
author: "<a href=https://www.andreashandel.com>Andreas Handel</a>"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    fig_caption: yes
vignette: >
  %\VignetteIndexEntry{shinyappsio_hosting}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---



```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7
)

# avoid check where vignette filename must equal the vignette title
options(rmarkdown.html_vignette.check_title = FALSE)
```


```{r, eval=TRUE, echo=FALSE}
#not able to use this in vignette of package unless i declare it in DESCRIPTION
#Currently not a CRAN package, os can't use in DESCRIPTION
#library('emo')
```



## Overview

This document describes hosting the grading app on shinyapps.io.



The following assumes that you will be hosting the submission system on RStudio's `shinyapps.io` service. For alternatives, see the end of the document.
One problem with `shinyapps.io` is the fact that you can't easily store files.

You can deploy everything with this command.

```{r, eval=FALSE, echo=TRUE}
deploy_quizgrader()
```

This function takes the submission app file, the 
and places them to the Shiny server. Students should now be able to go to the website (e.g. shinyapps.io`) and, after entering their identifying information, upload their quiz. 




## Using the grading system with shinyapps.io


The submission will be checked to make sure it is not past the due date or the number of allowed submissions has been exceeded. Then the quiz is graded by comparing the student submissions with those in the complete quiz files, the grade is recorded in the form of a score, and students are provided with immediate feedback on which questions they did get right and which they didn't. Anything entered into the `feedback` column is also displayed. In addition, students can see information about their cumulative performance so far. 

Note that as long as any password is missing from the student list, the app will display a `not ready for submission` message. 


## Storing and retrieving submissions

One

https://shiny.rstudio.com/articles/persistent-data-storage.html


