---
title: "Ongoing quiz management"
author: "<a href=https://www.andreashandel.com>Andreas Handel</a>"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    fig_caption: yes
vignette: >
  %\VignetteIndexEntry{quiz_administration}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---



```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7
)

# avoid check where vignette filename must equal the vignette title
options(rmarkdown.html_vignette.check_title = FALSE)
```


```{r, eval=TRUE, echo=FALSE}
#not able to use this in vignette of package unless i declare it in DESCRIPTION
#Currently not a CRAN package, os can't use in DESCRIPTION
#library('emo')
```



## Overview

This describes ongoing administration of the class list and quizzes while the course is running.


### Updating materials

If you need to make updates to either the main `gradelist.xlsx` file or the complete quizzes on the server, proceed as follows:

1. Make any modifications to the quizzes you need to make. Generate and distribute updated student versions.

2. During a time when students won't submit anything (e.g. right after a submission deadline or Saturday morning at 6am), download materials from the server.

3. FIND A WAY TO UPDATE GRADELIST.
 
CONTINUE HERE AND MAKE SURE THE ONLINE SUBMISSION SYSTEM WORKS


