---
title: "Analyzing quiz grades"
author: "<a href=https://www.andreashandel.com>Andreas Handel</a>"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    fig_caption: yes
vignette: >
  %\VignetteIndexEntry{quiz_analysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---



```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7
)

# avoid check where vignette filename must equal the vignette title
options(rmarkdown.html_vignette.check_title = FALSE)
```


```{r, eval=TRUE, echo=FALSE}
#not able to use this in vignette of package unless i declare it in DESCRIPTION
#Currently not a CRAN package, os can't use in DESCRIPTION
#library('emo')
```




### Retrieving and Analyzing student submissions

Once students start submitting, their grades are recorded in (always time-stamped and not overwritten) `gradelist.xlsx` files, and all their submissions, including their user ID and timestamp, are placed into the `studentsubmissions` folder. you'll want to pull files from the server every so often. Currently, this needs to be done manually. To that end, log into the shiny server and copy everything in the `studentsubmissions` and `gradelists` folders to the local versions of your course. Once done, open `quizmanager`, load the course you want to look at, and use the `Analyze Submissions` tab to see the performance of students and how the different quiz questions are being answered.  

